% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy
% \usepackage[document]{ragged2e}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Medhat Omr}
\newcommand{\CVTitle}{Medhat Omr's CV for Udacity 2018}
\newcommand{\CVNote}{CV compiled on {\today} for Udacity 2018}
\newcommand{\CVWebpage}{https://www.linkedin.com/in/medhatomr}
\newcommand{\github}{https://github.com/momr}

% PDF settings and properties.
% \usepackage{hyperref}

\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
% pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
% colorlinks   = true,
breaklinks
}


% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

% \hypersetup{linkcolor=blue,
% urlcolor  = blue}

\begin{SubTitle}
{Calgary, AB, Canada}
\par
\href{mailto:medhat.omr@gmail.com}
{medhat.omr@gmail.com}
\,\SubBulletSymbol\,
+1\,(403)\,918-7512
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{LinkedIn}}
\,\SubBulletSymbol\,
\href{\github}
{\url{GitHub}}
\end{SubTitle}

\begin{Body}



%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\Section
{Interests}
{Interests}
{PDF:Interests}

\Entry
Machine Learning (Statistical methods, and Deep Learning),
Data Science and Big Data, 
Self-Driving Cars related skills such as Localization, Control, Path Planning, Navigation, and Computer Vision.



%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}


\Entry
% \href{http://www.queensu.ca/}
{\textbf{Queen's University}},
Kingston, ON, Canada. 
\hfill
\DatestampYMD{2011}{09}{15} --
\DatestampYMD{2015}{03}{15}

\Gap
Ph.D. in 
% \href{http://my.ece.queensu.ca/}
{Electrical \& Computer Engineering}
\hfill
GPA 4.15
\BulletItem
Advisor: Prof. 
% \href{http://my.ece.queensu.ca/People/AboelmagdNoureldin/index.html}
{Aboelmagd Noureldin}


\BigGap
\Entry
% \href{http://www.asu.edu.eg/}
{\textbf{Ain Shams University}},
Cairo, Egypt. 
\hfill
\DatestampYMD{2003}{09}{15} --
\DatestampYMD{2008}{06}{15}

\Gap
B.Sc. in 
% \href{https://eng.asu.edu.eg/}
{Computer \& Systems Engineering }
\hfill
GPA 3.95/4
\BulletItem
Class rank: 3 of 140



%%%%%%%%%%%%%%%%%%%%%%%%%
%% EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Experience}
{Experience}
{PDF:Experience}

\Entry
% \href{http://www.tdk.com/index.php}
{\textbf{TDK}}, Canada

\Gap
Staff Algorithm Engineer, Navigation R\&D
\hfill
\DatestampYMD{2017}{10}{15} --
Present
\BulletItem
Products:
T-PN ME, \href{http://www.coursasports.com/}{CoursaSports}, and Driving Navigation related R\&D project
\BulletItem
In addition to the products above, I also build and maintain helping tools mainly\newline 
written in C++14, and Python

\Gap
Sr. Software Algorithm Designer, Navigation R\&D
\hfill
\DatestampYMD{2015}{04}{15} --
\DatestampYMD{2017}{09}{15}
\BulletItem
Products:
\href{http://www.coursasports.com/}{CoursaSports}
\BulletItem
In addition to the product above, I also built one internal library from scratch in C,\newline
and rewrite another big library from C into C++14 for another application

\BigGap
Software Algorithm Designer, Navigation R\&D
\hfill
\DatestampYMD{2012}{06}{15} --
\DatestampYMD{2015}{03}{15}
\BulletItem
Products: T-PN ME
\BulletItem
Some tasks that I did in T-PN ME include: 
\begin{Detail}
\SubBulletItem
\textbf{Algorithms Development} including collecting data, performing data wrangling, visualization, and analysis. In addition to developing and testing code in MATLAB

\SubBulletItem
\textbf{T-PN (ME) Integration} involving converting MATLAB code into C and integrate it into T-PN (ME), then test the integrated system on the initial data set. 

\SubBulletItem
\textbf{Algorithms Verification} through Deployment on one or more consumer devices, and test system on a wider users and devices base.
\end{Detail}

\BulletItem
For more details, please see Chapter 3 of my Ph.D. thesis in this \href{https://qspace.library.queensu.ca/bitstream/handle/1974/12804/Omr_Medhat_201504_PhD.pdf?sequence=1}{[link]} on what was my rule in T-PN ME product line

%%%%%%%%%%%%%%%%%%%%%%%%%
%% Online Education %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Online \newline
Education}
{Online Education}
{PDF:OnlineEducation}

\Entry
% \href{https://www.udacity.com/drive}
{\textbf{Udacity}},
Self-Driving Car Engineer Online Nanodegree
\hfill
\DatestampYMD{2017}{01}{15} --
\DatestampYMD{2018}{01}{15}

\Gap
% \href{https://medium.com/self-driving-cars/term-1-in-depth-on-udacitys-self-driving-car-curriculum-ffcf46af0c08}
{Over 15 projects in one year}

\BulletItem
Using deep learning to solve Traffic Sign Classification, and Driver Behaviour Cloning problems
\BulletItem
Using Computer Vision to implement an Advanced Lane Detection
\BulletItem
Using Machine Learning algorithms such as SVM, Decision Trees, and Ensemble Learning to solve Vehicle Tracking problem

% \href{https://medium.com/udacity/term-2-in-depth-on-udacitys-self-driving-car-curriculum-775130aae502}
\BulletItem
Implement a complete library in C++ for Extended Kalman Filter, Unscented Kalman Filter, and Particle Filter
\BulletItem
Control a vehicle to move it on a path in a simulation environment using PID Controller and Model-Predictive Controller (MPC)

% \href{https://medium.com/udacity/term-3-in-depth-on-udacitys-self-driving-car-curriculum-15d03e45d7ea}
\BulletItem
Implementing a Highway Path Planner involving Environmental Prediction, Behavior Planning, and Trajectory Generation
\BulletItem
Implementing Semantic Segmentation using Fully Convolutional Networks, Scene Understanding, and Inference Optimizations


%%%%%%%%%%%%%%%%%%
%% Computer Skills %%
%%%%%%%%%%%%%%%%%%

\Section
{Computer \newline
Skills}
{Computer Skills}
{PDF:Computer Skills}

\Entry
Languages: C, C++11, Python, and MATLAB

\Entry
Libraries: Scikit-learn, OpenCV, Keras, Tensorflow, TensorFlow Object Detection API, and PyTorch

\Entry
Other Tools/Services: Git, GitHub, CMake, and AWS

\pagebreak

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\Section
{Publications}
{Publications}
{PDF:Publications}

\SubSection
{Patents}
{Patents}
{PDF:Patents}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[8]}

\Gap
\NumberedItem{[1]}
Inventors: J. Georgy, Y. Li, \textbf{M. Omr} C. Goodall, H. Chang, Assignee: Invensense Inc., “Method and system for multiple pass smoothing”, Patent US9719787B2, Issued: Aug 1, 2017.

\Gap
\NumberedItem{[2]}
Inventors: \textbf{M. Omr}, J. Georgy, ad A. Noureldin, Assignee: Invensense Inc., “Method and System for Characterization of on Foot Motion with Multiple Sensor Assemblies”, Provisional Patent U.S. Serial No. 14/617,743, filing date: 9 February 2015.

\Gap
\NumberedItem{[3]}
Inventors: \textbf{M. Omr}, J. Georgy, and A. Noureldin, Assignee: Trusted Positioning Inc., “Method and Apparatus for Enhanced Navigation with Multiple Sensor Assemblies”, PCT application, International Application No. PCT/CA2014/000698, filing date: 17 September 2014 (priority by Provisional Patent U.S. Serial No. 61/878,952, filing date: 17 September 2013).

\Gap
\NumberedItem{[4]}
Inventors: J. Georgy, \textbf{M. Omr}, and A. Noureldin, Assignee: Trusted Positioning Inc., “Method and Apparatus for Determination of Misalignment between Device and Vessel Using Radius of Rotation”, PCT application, International Application No. PCT/CA2014/000670, filing date: 8 September 2015 (priority by Provisional patent U.S. Serial No. 61/878,336, filing date: 16 September 2013).

\Gap
\NumberedItem{[5]}
Inventors: \textbf{M. Omr}, A. Wahdan, J. Georgy, and A. Noureldin, Assignee: Trusted Positioning Inc., “Method and Apparatus for Varying Step Length Estimation Using Nonlinear System Identification”, U.S. Serial No. 14/764,519, filing date: 29 July 2015; PCT application, International Application No. PCT/CA2014/000060, filing date: 30 January 2014 (priority by Provisional patent U.S. Serial No. 61/759,522, filing date: 1 February 2013).


\endgroup

\BigGap

\SubSection
{Journals}
{Journals}
{PDF:Journals}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[8]}

\Gap
\NumberedItem{[1]}
% \href{https://doi.org/10.1007/s10291-016-0531-3}
{\textbf{M. Omr}, J. Georgy, and A. Noureldin,
``Using Multiple Portable/Wearable Devices for Enhanced Misalignment Estimation in Portable Navigation,''
\textit{GPS Solutions, Springer},
vol.~21,
no.~2,
pp.~393--404,
\DatestampYM{2017}{04}.}

\endgroup

\BigGap
\SubSection
{Conferences}
{Conferences}
{PDF:Conferences}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[8]}

\Gap
\NumberedItem{[1]}
% \href{http://www.example.com/my-paper-doi-3}
{\textbf{M. Omr}, J. Georgy, A. Noureldin,
``Using Multiple Sensor Triads for Enhancing the Navigation Solution of Portable and Wearable Devices,''
in \textit{ION GNSS+ 2013},
Nashville, USA,
\DatestampYM{2013}{09}.}

\Gap
\NumberedItem{[2]}
% \href{http://www.example.com/my-paper-doi-3}
{A. Wahdan, \textbf{M. Omr}, J. Georgy, A. Noureldin,
``Varying Step Length Estimation Using Nonlinear System Identification,''
in \textit{ION GNSS+ 2013},
Nashville, USA,
\DatestampYM{2013}{09}.}

\Gap
\NumberedItem{[3]}
\href{https://doi.org/10.1109/PLANS.2014.6851485}
{\textbf{M. Omr}, J. Georgy, A. Noureldin,
``Using Multiple Sensor Triads for Enhancing the Misalignment Estimation of a Navigation Solution of Portable and Wearable Devices,''
in \textit{IEEE/ION PLANS 2014},
California, USA,
\DatestampYM{2014}{05}.}

\Gap
\NumberedItem{[4]}
% \href{http://www.example.com/my-paper-doi-3}
{\textbf{M. Omr}, J. Georgy, W. Abdelfatah, D. Auld, and Z. Shen,
``T-PN ME: An Enhanced Real-Time Indoor/Outdoor Navigation System Using Multiple Portable/Wearable Devices,''
in \textit{ION GNSS+ 2014},
Tampa, USA,
\DatestampYM{2014}{09}.}

\Gap
\NumberedItem{[5]}
% \href{http://www.example.com/my-paper-doi-3}
{A. S. Ali, \textbf{M. Omr}, A. Al-Hamad, J. Georgy,
``Portable Real-time Indoor/Outdoor Navigation for Runners using Smart Devices,''
in \textit{ION GNSS+ 2014},
Tampa, USA,
\DatestampYM{2014}{09}.}

\endgroup

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Honors}
{Awards \& Honors}
{PDF:AwardsAndHonors}

\BulletItem
Mitacs and NSRC Awards, Electrical and Computer Engineering, Queens University 
\hfill
\DatestampY{2012} --
\DatestampY{2015}
\begin{Detail}
\Item
For successfully doing research in partnership with an industrial partner.
\end{Detail}

\Gap
\BulletItem
200\% working hours Award, Computer and Systems Engineering, Ain Shams University
\hfill
\DatestampYMD{2010}{05}{10}
\begin{Detail}
\Item
for outstanding achievement as a Teaching Assistant
\end{Detail}

\Gap
\BulletItem
Promoted from Private to Corporal Rank, Egyptian Military Forces, 
\hfill
\DatestampYMD{2010}{01}{15}
\begin{Detail}
\Item
for developing a data-driven application (using C\# and MS SQL) besides my normal duties as a soldier\newline
during my compulsory military service
\end{Detail}


\end{Body}

% %%%%%%%%%%%
% % CV NOTE %
% %%%%%%%%%%%

% \UseNoteFont%
% \null\hfill%
% [\textit{\CVNote}]

\end{document}
